### 2007-01-10 Documentation/part2.tex
*** empty log message ***

Furthermore, the matter density profile along the baseline
has to be specified. The simplest matter density profile is a constant matter density profile with the average matter density from the PREM~\cite{Stacey} onion shell model of the earth\index{norm}{PREM| \see{Matter density}}
\index{norm}{Matter density!of the earth}:
\begin{quote}
{\tt \$profiletype=1 }
\end{quote}
%
If your using this option please cite reference~\cite{Stacey}\index{norm}{Referencing!matter profile data}.

@@

A simple channel definition in \GLOBES\ consists of the flux,
the CP-sign of the initial state, the initial flavor, the final flavor,
the cross sections, and the energy resolution function. In order to refer to
flux, cross sections, and energy resolution functions, they have to be 
defined before with their {\tt \#name} in the respective environments. 
Thus, a simple definition of a channel\index{aedl}{{\tt channel}} is
\begin{quote}
{\tt channel(\#channel\_1)<\\
\tb @channel = \#flux : $+$: muon: muon: \#cross: \#energy\\
>}
\end{quote}
%
\index{norm}{Oscillation!switching off}
It is also possible to define a channel as no-oscillation by using the
prefix {\tt NOSC\_}\index{aedl}{{\tt channel}!{\tt NOSC\_}} 
in either the initial  flavour or 
the final flavour, like this
\begin{quote}
{\tt channel(\#channel\_1)<\\
\tb @channel = \#flux : $+$: NOSC\_muon: muon: \#cross: \#energy\\
>}
\end{quote}
%
In this case all diagonal probabilities $P_{\alpha\alpha}$ are unity, and all off-diagonal probablities  $P_{\alpha\beta}$ are zero. This is,
for instance, useful for
neutral current events, since these do not depend on any oscillation 
parameters\footnote{At least in the absence of sterile neutrinos}. The channels
marked as {\tt NOSC\_} are already computed by \GLB{SetRates}
and do not have to be recomputed in the subsequent fit (which calls the undocumented function \GLB{SetNewRates}).
Therefore this feature can be used to speed up the rate 
computation considerably, especially in cases where a large set
of channels exist which are only used for the computation of backgrounds.
Usually it is an excellent approximation to treat backgrounds as if they
were not affected by oscillations\footnote{In case, the backgrounds have
a sizeable dependence on the oscillation parameters they carry information
on the oscillation parameters and are therefore more like a signal.}.

@@

The energy resolution function $R^c(E,E')$ has been already introduced in 
\Sec~\ref{sec:channel}, where a definition
has been given in \eq~(\ref{eq:e_res}). Instead of using
 \eq~(\ref{eq:e_res}) directly, we apply a slightly different
definition of the post-smearing efficiencies $\epsilon(E')$. 
In general, $\epsilon(E')$ has to be
determined by means of a Monte Carlo simulation of the experiment. 
This usually involves a binning of the simulated events in the 
reconstructed energy $E'$. Therefore, one simplify \eq~(\ref{eq:events_bin}) by
\begin{equation}
\label{eq:post_smearing}
\int_{E_i-\Delta E_i/2}^{E_i+\Delta E_i/2} dE' \, R^c(E,E') \, \epsilon^c(E')
 \simeq \hat\epsilon_i^c \cdot \int_{E_i-\Delta E_i/2}^{E_i+\Delta E_i/2} dE' 
\quad R^c(E,E')\,.
\end{equation}
Here the  $\hat\epsilon_i^c$ are the 
binned ``post-smearing'' efficiencies, which will be set within the corresponding {\tt channel} environment (see below).
From \eq~(\ref{eq:events_bin}) it is obvious that the integration with respect to the reconstructed energy $E'$ can be
performed independently of the oscillation parameters. We define
the ``bin kernel'' $K_i^c$ for the $i$th bin as
\begin{equation}
\label{eq:kernel}
K_i^c(E) \equiv \int_{E_i-\Delta E_i/2}^{E_i+\Delta E_i/2} dE' 
\quad R^c(E,E')\,.
\end{equation}
With this definition, \eq~(\ref{eq:events_bin}) can be re-written as
\begin{equation}
\label{eq:simple_int}
n_i^c=N/L^2 \,
\hat\epsilon_i^c \, \int\limits_0^\infty dE\quad  \underbrace{\Phi^c(E)\,
P^c(E)\,
\sigma^c(E) \, K_i^c(E)\,}_{f(E)}. 
\end{equation}

@@

Before we come to the calculation algorithms, it is useful to understand
the general evaluation algorithm. As it is illustrated in \figu{energies}, 
\GLOBES\ uses several levels with respect to the energy ranges:
\begin{description}
\item[Sampling point level]
 This level is used internally to evaluate the integrand in \eq~(\ref{eq:simple_int}) at all sampling points. The energy scale is the actual incident neutrino energy $E$. 
For a manual definition of the sampling points, use
\index{aedl}{sampling points@{\tt \$sampling\_points}}
\index{aedl}{sampling min@{\tt \$sampling\_min}}
\index{aedl}{sampling max@{\tt \$sampling\_max}}
\begin{quote}
{\tt
\$sampling\_points = 20\\
\$sampling\_min =          4.0\\
\$sampling\_max =         50.0
}
\end{quote}
for equidistant sampling points. If no values are given for these variables
they are assumed to be equal to their corresponding counter part at bin level,
\ie\ \verb+$sampling_points = $bins+, \verb+$sampling_min = $emin+ and
\verb+$sampling_max = $emax+.

Arbitrarily spaced sampling points can 
be specified with 
{\tt \$sampling\_stepsize}\index{aedl}{sampling stepsize@{\tt \$sampling\_stepsize}}
\begin{quote}
{\tt
\$sampling\_stepsize=\{1.0,2.0,3.0,4.0,5.0,...\}
}
\end{quote}
The choice of the sampling point configuration strongly depends on the 
experiment and required accuracy. Ideally the integrand 
of~\eq~\ref{eq:simple_int} is zero outside the sampling range, if this cannot
be achieved it is usually sufficient that the sampling range is by about
three times the energy resolution\footnote{evaluated at {\tt \$emin} and
{\tt \$emax} respectively} larger than the bin range. 
The spacing of the sampling points should be somewhat smaller (a factor 
$\simeq 2$ usually is more than ebough) than the 
finest details of the integrand.

@@

In the following subsections we will define the energy resolution function.
All energy resolution functions are defined within an {\tt energy} environment and can be refered to by {\tt \#name}.
\begin{quote}
  {\tt energy(\#name)<\\
\tb $\ldots$\\
>}
\end{quote}
The individual parameters of the environment will be defined below and depend on the algorithm used.

@@

In the actual implementation of the algorithm,  the sum in \eq~(\ref{eq:algo_one}) is only computed for the $E_j$'s where $K(E_j)$ 
is above a certain threshold, which is by default $10^{-7}$. 
This threshold is defined at the compiling time.

@@

Now we can introduce the different systematical errors. 
The two most important and
most easily parameterized systematical errors are the normalization 
and an energy calibration errors. These errors are assumed to be independent between the signal events and the background events, which means that
this systematics treatment defines the grouping into signal or background.
The implementation of the normalization error
is straightforward:
\begin{equation}
s_i(a):=a\cdot s_i
\end{equation} 
with an analogous definition for the background events. Here, $a$ is the``nuisance'' parameter, which will be minimized over later.

For the parameterization of an energy calibration error, two possibilities
are implemented. The first one (method ``T'') is somewhat simpler, 
whereas the second one (method ``C'')
is more accurate, but it requires a careful choice of parameters. 
The first option (method ``T'') is
\begin{equation}
s_i(a,b) \equiv s_i(a)+b\cdot s_i\, E'_i/(E'_\mathrm{max}-E'_\mathrm{min}),
\end{equation}
where $E'_{\mathrm{min}}$ and $E'_{\mathrm{max}}$ correspond to {\tt \$emin}
and {\tt \$emax}, and $E'_i$ is the mean (reconstructed) 
energy of the $i$th bin. It is often refered to as a ``tilt'' of the
spectrum, since it describes a linear distortion 
of the event rate spectrum. Note that this definition of a tilt makes
only sense in combination with a large enough normalization error, since
the tilt also affects the normalization.
%
The second option (method ``C'') is closer to an actual energy
calibration error, which means that one should test this option whenever
one suspects a large impact of this systematical error.
It is based upon replacing the events in the $i$th bin by the ones at
the energy $(1+b)\cdot E'_i$. If this target energy does not exactly hit
a (discrete) bin energy $E_k$, linear interpolation is used. We use the following approximation:
\begin{eqnarray}
s_i(a,b)&=& (1+b)\cdot \left[ \left( s_{k+1}(a)-s_k(a) \right)\cdot (\delta-k) +s_k(a) \right] \,,\\
\delta&=&b\cdot(i+t_0+ 1/2)+i\,,\nonumber\\
k&=& \mathrm{div}(\delta,1)\,,\nonumber\\
t_0&=&E'_\mathrm{min}/\Delta E_0\,.\nonumber
\end{eqnarray}
Here $\Delta E_0$ is the bin width ({\tt \$emax}-{\tt \$emin})/{\tt \$bins}
and ``div'' refers to the integer part of the division. Note that the
factor $(1+b)$ in the first equation comes from a renormalization of
the bin width, since also the bin width is altered by the replacement of
the energies. Furthermore, special care has to be payed to the limits
 $k<1$ or $k+1>N_\mathrm{bins}$, since there $s_k$ or $s_{k+1}$ may not have been calculated. By default, it is assumed that $s_k$ is
zero in those cases. However, if the event rates are still large at
the limits, errors will be introduced leading to a wrong
estimate of the impact of the calibration error. In this case,
one should truncate the analysis range by a few bins at the boundaries
and therefore ensure in this way that only those $s_i$ are used whose index
$k$ is within the range $0,\ldots, N_\mathrm{bins}-1$ (\cf, \figu{energies}). 
Thus, it is possible to constrain the analysis energy range 
with each rule to an energy window\index{norm}{Energy!window}:
\index{aedl}{{\tt rule}!energy window@{\tt "@energy\_window}}
\begin{quote}
{\tt 
\tb @energy\_window = 4.0 : 50.0 
}
\end{quote}
The default energy window is given between the minimal and maximal reconstructed energy. To be on the save side, reduce analysis window
compared to the bin range on each side by about three times the
energy calibration error.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
\begin{table}[t!]
\begin{center}
\begin{tabular}[h]{|c|cccc|c|l|}
\hline
Error dimension&$a$&$b$&$c$&$d$&Tilt/Calibration&Remarks\\
\hline
\hline
0&+&+&+&+&T&Systematics with tilt\\
2&-&-&-&-&-&No systematics\\
4&+&+&+&+&T&Total rates\\
7& $\infty$ &-& $\infty$ &-&-&Spectrum only\\
8&-&-&-&-&-&Total rates, no systematics\\
9&+&+&+&+&C&Systematics with calibration\\
20&?&?&?&?&?&User-defined systematics\\
\hline
\end{tabular}
\mycaption[Table of error dimensions]{\label{tab:error_dim}
Possible values of the error dimensions variable in \GLOBES\ and their meaning. If a parameter is designated with $+$, it will
be marginalized over, and therefore the corresponding error needs to 
have a non-zero value. If the cases with ``total rates'' in the remarks, 
the summation over the bins is performed \emph{before} computing 
the $\chi^2$, \ie, no spectral information is used. 
The error dimension~7 ``spectrum only'' leaves the 
normalization free ($\sigma_a=\sigma_c=\infty$), and therefore 
only the spectral information is used. As a consequence,
the settings for the normalization error will be ignored (designated 
with the symbol $\infty$).

 }
\end{center}
\index{aedl}{{\tt rule}!errordim@{\tt "@errordim}} 
\end{table} 
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Eventually, a rule looks like
\begin{quote}
{\tt rule(\#rule\_1)<\\
\tb @signal = 0.5 @ \#channel\_1\\
\tb @background = 0.001 @ \#channel\_2 :  0.005 @ \#channel\_3\\
\tb @signalerror =       0.001  :       0.01\\
\tb @backgroundcenter =  0.1 :       0.0\\
\tb @backgrounderror =   0.001 :       0.01\\
\tb @errordim\_sys\_off = 2\\
\tb @errordim\_sys\_on = 0\\
\tb @energy\_window = 4.0 : 50.0\\ 
>}
\end{quote}
\index{aedl}{{\tt rule}|)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Version control in \AEDL\ files}
\label{sec:aedl_versioning}
\index{norm}{Version control}

In order to avoid problems which come from different
versions of \GLOBES\ and \AEDL\ files, it is possible to use in each 
\AEDL\ file a version number. For example, it may correspond to the  minimum version number of the \GLOBES\ package with which it works. Set the
{\tt \$version}\index{aedl}{version@{\tt \$version}} by
\begin{quote}
{\tt \$version="1.8.1"}
\end{quote}
This information can be accessed by the versioning functions as described in~\Sec~\ref{sec:versioning}.
\index{norm}{AEDL@\AEDL|)}

>>>>

Furthermore, the matter density profile along the baseline
has to be specified. The simplest matter density profile is a constant matter density profile with the average matter density from the PREM~\cite{Stacey} onion shell model of the earth:\index{norm}{PREM| \see{Matter density}}
\index{norm}{Matter density!of the earth}
\begin{quote}
{\tt \$profiletype=1 }
\end{quote}
%
If your using this option please cite reference~\cite{Stacey}\index{norm}{Referencing!matter profile data}.

@@

A simple channel definition in \GLOBES\ consists of the flux,
the CP-sign of the initial state, the initial flavor, the final flavor,
the cross sections, and the energy resolution function. In order to refer to
flux, cross sections, and energy resolution functions, they have to be 
defined before with their {\tt \#name} in the respective environments. 
Thus, a simple definition of a channel\index{aedl}{{\tt channel}} is
\begin{quote}
{\tt channel(\#channel\_1)<\\
\tb @channel = \#flux : $+$: muon: muon: \#cross: \#energy\\
>}
\end{quote}
%
\index{norm}{Oscillation!switching off}
It is also possible to define a channel as no-oscillation by using the
prefix {\tt NOSC\_}\index{aedl}{{\tt channel}!{\tt NOSC\_}} 
in either the initial  flavour or 
the final flavour, like this
\begin{quote}
{\tt channel(\#channel\_1)<\\
\tb @channel = \#flux : $+$: NOSC\_muon: muon: \#cross: \#energy\\
>}
\end{quote}
%
In this case all diagonal probabilities $P_{\alpha\alpha}$ are unity, and all off-diagonal probablities  $P_{\alpha\beta}$ are zero. This is,
for instance, useful for
neutral current events, since these do not depend on any oscillation 
parameters\footnote{At least in the absence of sterile neutrinos}. The channels
marked as {\tt NOSC\_} are already computed by \GLB{SetRates}
and do not have to be recomputed in the subsequent fit (which calls the undocumented function \GLB{SetNewRates}).
Therefore this feature can be used to speed up the rate 
computation considerably, especially in cases where a large set
of channels exist which are only used for the computation of backgrounds.
Usually it is an excellent approximation to treat backgrounds as if they
were not affected by oscillations\footnote{In the case that the backgrounds have
a sizeable dependence on the oscillation parameters, they carry information
on the oscillation parameters, and therefore behave more like a signal.}.

@@

The energy resolution function $R^c(E,E')$ has been already introduced in 
\Sec~\ref{sec:channel}, where a definition
has been given in \eq~(\ref{eq:e_res}). Instead of using
 \eq~(\ref{eq:e_res}) directly, we apply a slightly different
definition of the post-smearing efficiencies $\epsilon(E')$. 
In general, $\epsilon(E')$ has to be
determined by means of a Monte Carlo simulation of the experiment. 
This usually involves a binning of the simulated events in the 
reconstructed energy $E'$. Therefore, one can simplify \eq~(\ref{eq:events_bin}) by
\begin{equation}
\label{eq:post_smearing}
\int_{E_i-\Delta E_i/2}^{E_i+\Delta E_i/2} dE' \, R^c(E,E') \, \epsilon^c(E')
 \simeq \hat\epsilon_i^c \cdot \int_{E_i-\Delta E_i/2}^{E_i+\Delta E_i/2} dE' 
\quad R^c(E,E')\,.
\end{equation}
Here the  $\hat\epsilon_i^c$ are the 
binned ``post-smearing'' efficiencies, which will be set within the corresponding {\tt channel} environment (see below).
From \eq~(\ref{eq:events_bin}) it is obvious that the integration with respect to the reconstructed energy $E'$ can be
performed independently of the oscillation parameters. We define
the ``bin kernel'' $K_i^c$ for the $i$th bin as
\begin{equation}
\label{eq:kernel}
K_i^c(E) \equiv \int_{E_i-\Delta E_i/2}^{E_i+\Delta E_i/2} dE' 
\quad R^c(E,E')\,.
\end{equation}
With this definition, \eq~(\ref{eq:events_bin}) can be re-written as
\begin{equation}
\label{eq:simple_int}
n_i^c=N/L^2 \,
\hat\epsilon_i^c \, \int\limits_0^\infty dE\quad  \underbrace{\Phi^c(E)\,
P^c(E)\,
\sigma^c(E) \, K_i^c(E)\,}_{f(E)}. 
\end{equation}

@@

Before we come to the calculation algorithms, it is useful to understand
the general evaluation algorithm. As it is illustrated in \figu{energies}, 
\GLOBES\ uses several levels with respect to the energy ranges:
\begin{description}
\item[Sampling point level]
 This level is used internally to evaluate the integrand in \eq~(\ref{eq:simple_int}) at all sampling points. The energy scale is the actual incident neutrino energy $E$. 
For a manual definition of the sampling points, use
\index{aedl}{sampling points@{\tt \$sampling\_points}}
\index{aedl}{sampling min@{\tt \$sampling\_min}}
\index{aedl}{sampling max@{\tt \$sampling\_max}}
\begin{quote}
{\tt
\$sampling\_points = 20\\
\$sampling\_min =          4.0\\
\$sampling\_max =         50.0
}
\end{quote}
for equidistant sampling points. If no values are given for these variables,
they are assumed to be equal to their corresponding counter parts at the bin level,
\ie , \verb+$sampling_points = $bins+, \verb+$sampling_min = $emin+ and
\verb+$sampling_max = $emax+.

Arbitrarily spaced sampling points can 
be specified with 
{\tt \$sampling\_stepsize}\index{aedl}{sampling stepsize@{\tt \$sampling\_stepsize}}
\begin{quote}
{\tt
\$sampling\_stepsize=\{1.0,2.0,3.0,4.0,5.0,...\}
}
\end{quote}
The choice of the sampling point configuration strongly depends on the 
experiment and required accuracy. Ideally, the integrand 
of~\eq~\ref{eq:simple_int} is zero outside the sampling range. If this cannot
be achieved, it is usually sufficient that the sampling range is by about
three times the energy resolution (evaluated at {\tt \$emin} and
{\tt \$emax}, respectively) larger than the bin range. 
The spacing of the sampling points should be somewhat smaller than the 
finest details of the integrand (a factor 
$\simeq 2$ usually is more than enough).

@@

In the following subsections we will define the energy resolution function.
All energy resolution functions are defined within an {\tt energy} environment and can be refered to by {\tt \#name}:
\begin{quote}
  {\tt energy(\#name)<\\
\tb $\ldots$\\
>}
\end{quote}
The individual parameters of the environment will be defined below and depend on the algorithm used.

@@

In the actual implementation of the algorithm,  the sum in \eq~(\ref{eq:algo_one}) is only evaluated
 for the $E_j$'s with $K(E_j)$ 
above a certain threshold, which is, by default, $10^{-7}$. 
This threshold is defined at the compiling time.

@@

Now we can introduce the different systematical errors. 
The two most important and
most easily parameterized systematical errors are the normalization 
and an energy calibration errors. These errors are assumed to be independent between the signal events and the background events, which means that
this systematics treatment defines the grouping into signal or background.
The implementation of the normalization error
is straightforward:
\begin{equation}
s_i(a):=a\cdot s_i
\end{equation} 
with an analogous definition for the background events. Here, $a$ is the ``nuisance'' parameter, which will be minimized over later.

For the parameterization of an energy calibration error, two possibilities
are implemented. The first one (method ``T'') is somewhat simpler, 
whereas the second one (method ``C'')
is more accurate, but it requires a careful choice of parameters. 
The first option (method ``T'') is (JK: IS THAT CORRECT? AND ALSO THE NEXT EQUATION? (THERE HAVE BEEN
SOME CHANGES) [WW])
\begin{equation}
s_i(a,b) \equiv s_i(a)+b\cdot s_i\, E'_i/(E'_\mathrm{max}-E'_\mathrm{min}),
\end{equation}
where $E'_{\mathrm{min}}$ and $E'_{\mathrm{max}}$ correspond to {\tt \$emin}
and {\tt \$emax}, and $E'_i$ is the mean (reconstructed) 
energy of the $i$th bin. It is often refered to as a ``tilt'' of the
spectrum, since it describes a linear distortion 
of the event rate spectrum. Note that this definition of a tilt makes
only sense in combination with a large enough normalization error, since
the tilt also affects the normalization.
%
The second option (method ``C'') is closer to an actual energy
calibration error, which means that one should test this option whenever
one suspects a large impact of this systematical error.
It is based upon replacing the events in the $i$th bin by the ones at
the energy $(1+b)\cdot E'_i$. If this target energy does not exactly hit
a (discrete) bin energy $E_k$, linear interpolation is used. We use the following approximation:
\begin{eqnarray}
s_i(a,b)&=& (1+b)\cdot \left[ \left( s_{k+1}(a)-s_k(a) \right)\cdot (\delta-k) +s_k(a) \right] \,,\\
\delta&=&b\cdot(i+t_0+ 1/2)+i\,,\nonumber\\
k&=& \mathrm{div}(\delta,1)\,,\nonumber\\
t_0&=&E'_\mathrm{min}/\Delta E_0\,.\nonumber
\end{eqnarray}
Here $\Delta E_0$ is the bin width ({\tt \$emax}-{\tt \$emin})/{\tt \$bins}
and ``div'' refers to the integer part of the division. Note that the
factor $(1+b)$ in the first equation comes from a renormalization of
the bin width, since also the bin width is altered by the replacement of
the energies. Furthermore, special care has to be payed to the limits
 $k<1$ or $k+1>N_\mathrm{bins}$, since there $s_k$ or $s_{k+1}$ may not have been calculated. By default, it is assumed that $s_k$ is
zero in those cases. However, if the event rates are still large at
the limits, errors will be introduced leading to a wrong
estimate of the impact of the calibration error. In this case,
one should truncate the analysis range by a few bins at the boundaries
and therefore ensure in this way that only those $s_i$ are used whose index
$k$ is within the range $0,\ldots, N_\mathrm{bins}-1$ (\cf, \figu{energies}). 
Thus, it is possible to constrain the analysis energy range 
with each rule to an energy window\index{norm}{Energy!window}:
\index{aedl}{{\tt rule}!energy window@{\tt "@energy\_window}}
\begin{quote}
{\tt 
\tb @energy\_window = 4.0 : 50.0 
}
\end{quote}
The default energy window is given between the minimal and maximal reconstructed energy. To be on the save side, reduce analysis window
compared to the bin range on each side by about three times the
energy calibration error.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}[t!]
\begin{center}
\begin{tabular}[h]{|lccccccl|}
\hline
Systematics function &$a$&$b$&$c$&$d$&Tilt/Calibr.& Dim. & Remarks\\
\hline
\hline
\multicolumn{8}{|l|}{{\bf Standard systematics:}} \\
{\tt chiSpectrumTilt} &+&+&+&+&T&0&Systematics with tilt\\
{\tt chiNoSysSpectrum} &-&-&-&-&-&2&No systematics\\
{\tt chiTotalRatesTilt} &+&+&+&+&T&4&Total rates\\
{\tt chiSpectrumOnly} & $\infty$ &-& $\infty$ &-&-&7&Spectrum only\\
{\tt chiNoSysTotalRates} &-&-&-&-&-&8&Total rates, no syst.\\
{\tt chiSpectrumCalib} &+&+&+&+&C&9&ystematics with calibr.\\
\hline\multicolumn{8}{|l|}{{\bf User-defined systematics:}} \\
{\tt chiZero} & - & - & - & - & - & n/a & Passive rule\\
 & & & & & & & ($\chi^2$ returns zero) \\
Any other name & \multicolumn{5}{c}{User-defined behavior} & n/a & User-defined syst. \\
\hline
\end{tabular}
\mycaption[Table of error dimensions]{\label{tab:error_dim}
Possible systematics $\chi^2$ functions  in \GLOBES\ and their meaning. 
If a parameter is designated with $+$, it will
be marginalized over, and therefore the corresponding error needs to 
have a non-zero value. If the cases with ``total rates'' in the remarks, 
the summation over the bins is performed \emph{before} computing 
the $\chi^2$, \ie, no spectral information is used. 
The function {\tt chiSpectrumOnly} leaves the 
normalization free ($\sigma_a=\sigma_c=\infty$), and therefore 
only the spectral information is used. As a consequence,
the settings for the normalization error will be ignored (designated 
with the symbol $\infty$). In addition, the corresponding error
dimension from earlier versions of \GLOBES\ is shown in the column ``Dim.''.
 }
\end{center}
\index{aedl}{{\tt rule}!errordim@{\tt "@errordim}} 
\index{norm}{Systematics function} 
\end{table} 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Eventually, a rule looks like
\begin{quote}
{\tt rule(\#rule\_1)<\\
\tb @signal = 0.5 @ \#channel\_1\\
\tb @background = 0.001 @ \#channel\_2 :  0.005 @ \#channel\_3\\
\tb @signalerror =       0.001  :       0.01\\
\tb @backgroundcenter =  0.1 :       0.0\\
\tb @backgrounderror =   0.001 :       0.01\\
\tb @errordim\_sys\_off = 2\\
\tb @errordim\_sys\_on = 0\\
\tb @energy\_window = 4.0 : 50.0\\ 
>}
\end{quote}
\index{aedl}{{\tt rule}|)}

% THIS PART HAS GAINED IMPORTANCE AND THEREFORE BEEN EXPLAINED ALREADY IN THE LAST CHAPTER!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Version control in \AEDL\ files}
% \label{sec:aedl_versioning}
% \index{norm}{Version control}
% 
% In order to avoid problems which come from different
% versions of \GLOBES\ and \AEDL\ files, it is possible to use in each 
% \AEDL\ file a version number. For example, it may correspond to the  minimum version number of the \GLOBES\ package with which it works. Set the
% {\tt \$version}\index{aedl}{version@{\tt \$version}} by
% \begin{quote}
% {\tt \$version="1.8.1"}
% \end{quote}
% This information can be accessed by the versioning functions as described in~\Sec~\ref{sec:versioning}.
% \index{norm}{AEDL@\AEDL|)}
